\section{Link-State Advertisements}
\label{sec:lsas}

Link-State Advertisements (LSAs) represent pieces of routing information distributed by routers.
NLSR uses three types of LSAs to distribute routing information:
Adjacency LSAs which include neighboring node and link information,
Coordinate LSAs which include a router's hyperbolic coordinates, and
Name LSAs which include advertised name prefixes reachable through the router.
All of the LSAs received by the router are maintained by the LSDB module (Section~\ref{sec:lsdb}).

\subsection{LSA Base Class}
\label{sec:lsa-base-class}

All three LSA implementations inherit from an LSA Base class, \texttt{Lsa}, which maintains information that is included in each LSA.
The \texttt{LSA} class contains the following member variables:
\begin{itemize}
\item \textbf{Origin Router} - the router that advertised the LSA.
\item \textbf{Sequence Number} - a number used to indicate the LSAs version as well as its ordering compared to other LSAs received from the same router.
\item \textbf{Expiration Time Point} - a time point indicating when the LSA is no longer valid.
\end{itemize}

\subsection{Adjacency LSAs}
\label{sec:adjacency-lsas}

Adjacency LSAs maintain an \texttt{AdjacencyList} which contains all the currently \texttt{ACTIVE} neighbors of the origin router.

\subsection{Coordinate LSAs}
\label{sec:coordinate-lsas}

Coordinate LSAs maintain the hyperbolic angle(s) and hyperbolic radius of the origin router.

\subsection{Name LSAs}
\label{sec:name-lsas}

Name LSAs maintain a \texttt{NamePrefixList} which contains advertised name prefixes that are reachable through the origin router.